The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs

### 2022-03-09 src/paper/report.tex
Remove Smith2021 almost completely, use clipboard package.

We include two types of tests. Polymerase chain reaction (PCR) tests reveal whether an
individual is infected or not; there is no uncertainty to the result. PCR tests require
at least one day to be processed and there are aggregate capacity constraints. In
contrast, rapid antigen tests yield immediate results. Specificity and sensitivity of
these tests is set according to data analyzed in \cite{Bruemmer2021, Smith2021};
sensitivity depends on the timing of the test relative to the onset of infectiousness
(we show our results are robust to more conservative assumptions in
Section~\ref{subsec:robustness_rapid_test_sensitivity}). After a phase-in period, all
tests that are demanded will be performed. Figure~\ref{fig:model_rapid_tests} shows our
model for rapid test demand. Schools may require staff and students to be tested
regularly. Rapid tests may be offered by employers to on-site workers. Individuals may
demand tests for private reasons, which include having plans to meet other people,
showing symptoms of CoViD-19, and a household member having tested positively for the
virus. We endow each agent with an individual compliance parameter. This parameter
determines whether she takes up rapid tests.\footnote{Positive test results or symptoms
    lead most individuals to reduce their contacts; this is why tests impact the actual
    contacts in Figure~\ref{fig:model_description}.}

>>>>

We include two types of tests. Polymerase chain reaction (PCR) tests reveal whether an
individual is infected or not; there is no uncertainty to the result. PCR tests require
at least one day to be processed and there are aggregate capacity constraints. In
contrast, rapid antigen tests yield immediate results. Specificity and sensitivity of
these tests is set according to data analyzed in
\label{r.1.a}\Copy{r.1.a}{\cite{Bruemmer2021,Scheiblauer2021,Özcürümez2021};
    sensitivity depends on the timing of the test relative to the onset of infectiousness.}
After a phase-in period, all tests that are demanded will be performed.
Figure~\ref{fig:model_rapid_tests} shows our model for rapid test demand. Schools may
require staff and students to be tested regularly. Rapid tests may be offered by
employers to on-site workers. Individuals may demand tests for private reasons, which
include having plans to meet other people, showing symptoms of CoViD-19, and a household
member having tested positively for the virus. We endow each agent with an individual
compliance parameter. This parameter determines whether she takes up rapid
tests.\footnote{Positive test results or symptoms lead most individuals to reduce their
    contacts; this is why tests impact the actual contacts in
    Figure~\ref{fig:model_description}.}

### 2022-03-09 src/rev1_reply_comments.tex
Remove Smith2021 almost completely, use clipboard package.

\documentclass[a4paper,11pt]{article}
\usepackage{a4wide}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{afterpage,rotating,natbib,graphicx,setspace,xcolor}
\usepackage{longtable,booktabs,tabularx}
\usepackage{chngcntr}
\usepackage{eurosym,calc}
\usepackage{amsmath,amssymb,amsfonts,amsthm,delarray}
\usepackage{bm}
\usepackage{bbm}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{xfrac}
\usepackage{listings}
\usepackage{adjustbox}
\usepackage{xr}
\usepackage{xr-hyper}
\usepackage[unicode=true]{hyperref}
\usepackage{afterpage}
\usepackage{clipboard}

@@

@@

@@

\response{Many thanks for these insightful comments. We respond in three parts.}

\begin{enumerate}
    \item In part, incorrect references are also used, especially for the assumption of
          the high sensitivity of the rapid tests. For example, reference No. 74 explicitly
          does not refer to rapid antigen tests, but to an immunological laboratory test
          method (Quidel SARS Sofia antigen FIA).

          \response{%
              We would like to thank the reviewer for spotting this mistake of ours. We
              removed the reference.}

    \item In the development of the mathematical model, apparently only the knowledge
          available a few months ago on the performance of rapid antigen tests was taken into
          account.

          The authors should at least model this with an alternative calculation and
          discuss it accordingly. Such an improvement would increase the importance of
          this manuscript enormously.

          \response{%
              We agree that the references we used have become outdated in the meantime.
              Note that we submitted the original manuscript in early September 2021;
              the calculations had been done some time before that.

              We therefore ran additional simulations with updated and more conservative
              assumptions on the sensitivity of rapid tests (Appendix~\ref{subsec:robustness_rapid_test_sensitivity}) and found that
              our main results are remarkably robust to this change. The percentage of the
              decrease in spring 2021 attributed to rapid tests decreases by only 4
              percentage points even in the least favourable scenario. We describe our
              approach for calculating the adjusted sensitivities in the next answer. }
    \item I recommend including a declaration of potential conflicts of interest in the
          manuscript.
          \response{We have added such a declaration. There are no competing interests.}

\end{enumerate}
}

\section{Reviewer 2}

@@

% \setstretch{1} \bibliographystyle{ecta} \bibliography{refs}

>>>>

\documentclass[a4paper,11pt]{article}
\usepackage{a4wide}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{afterpage,rotating,graphicx,setspace,xcolor}
\usepackage{longtable,booktabs,tabularx}
\usepackage{chngcntr}
\usepackage{eurosym,calc}
\usepackage{amsmath,amssymb,amsfonts,amsthm,delarray}
\usepackage{bm}
\usepackage{bbm}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{xfrac}
\usepackage{listings}
\usepackage{adjustbox}
\usepackage{xr}
\usepackage{xr-hyper}
\usepackage[unicode=true]{hyperref}
\usepackage{afterpage}
\usepackage{clipboard}
\input{templates/Preamble_BibLaTeX_Science}
\openclipboard{clipboard-rev1}

@@

\bibliography{references.bib}

@@

\response{%
    We would like to thank the reviewer for these insightful comments. First of all, we
    agree that the references we used have become outdated in the meantime. Note that we
    submitted the original manuscript in early September 2021; the analysis had been
    finalised in June already.

    Many thanks for pointing out that we misclassified the Quidel SARS Sofia antigen
    FIA test; we removed the reference.

    Indeed, in the line of the additional evidence, the numbers we use for test
    sensitivity seem to be in the upper part of plausible values. On
    page~\pageref{r.1.a} of the paper, we cite the two references you pointed out (numbering of references as in this document):

    \textit{\Paste{r.1.a}}

    We therefore followed
    your suggestion and ran additional analyses with more conservative assumptions on
    the sensitivity of rapid tests. We report on these in
    Appendix~\ref{subsec:robustness_rapid_test_sensitivity}. Our results are
    remarkably robust to this change. We write:

    The percentage of the decrease in spring 2021
    attributed to rapid tests decreases by only 4 percentage points even in the least
    favourable scenario. We describe our approach for calculating the adjusted
    sensitivities in the next answer. }

@@

\response{We have added such a declaration. There are no competing interests.}

}

\clearpage
\section*{Reviewer 2}

@@

\begin{refcontext}[sorting=none]  % Sort BIBLIOGRAPHY by appearance.
    \printbibliography[heading=bibintoc]
\end{refcontext}
